Locating saddle points in complex and memory intensive landscapes

### 2022-02-24 manuscript.tex
Added exascale computing citations

\topic However, a large range of landscapes prove challenging or impossible to explore via these methods.
One key problem arises from the push towards larger and more complex systems \temp{[cite]}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different discretisation for each state.
Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
Both of which can be relevent when considering contact forces for macroscopic objects \temp{[cite]}, or hard-body interactions in atomistic systems \temp{[cite]}.
Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
Specialist treatment can sometimes be used such as in the case of global rotation and translation \temp{\cite{Wales2004}}, but they are thwarted by local zero-modes.
Meanwhile, current methods cannot typically be applied in the case of discontinuous potentials, or where the gradient is prohibitively expensive to compute, because they require continuous, differentiable optimisation functions.

>>>>

\topic However, a large range of landscapes prove challenging or impossible to explore via these methods.
One key problem arises from the push towards larger and more complex systems \cite{Trefethen2013,Shalf2020,Alexander2020}, resulting in the need to develop algorithms that are more memory and computationally efficient, and can incorporate optimisation strategies such as on-the-fly adaptive remeshing and coarse-graining.
Current double-ended methods require a chain of tens of states to gain an accurate approximation, and have issues with remeshing resulting in a different discretisation for each state.
Single-ended methods are not well suited for identifying specific pathways and can spend a large amount of time searching for undesired transition states.
Another major challenge in studying complex energy landscapes relates to the presence of locally flat or discontinous regions.
Both of which can be relevent when considering contact forces for macroscopic objects \temp{[cite]}, or hard-body interactions in atomistic systems \temp{[cite]}.
Flat zero-modes in the landscape pose issues for single-ended search methods that rely only upon local information.
Specialist treatment can sometimes be used such as in the case of global rotation and translation \temp{\cite{Wales2004}}, but they are thwarted by local zero-modes.
Meanwhile, current methods cannot typically be applied in the case of discontinuous potentials, or where the gradient is prohibitively expensive to compute, because they require continuous, differentiable optimisation functions.
